---
name: Dr Aidan Boland
position: "Senior Data Scientist"
#address: "..."
#phone: ...
#profilepic: profilecrop.jpg
www: aboland.ie
email: "aidansboland@gmail.com"
twitter: BolandAi
github: aboland
linkedin: aidanboland
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Data scientist with 4 years industry experience, and 5 years research experience."
fontsize: 11pt
output: 
  pdf_document: 
    keep_tex: no
    latex_engine: xelatex
    template: custom_template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```


# Employment

```{r}
library(tibble)
tribble(
  ~ Title, ~ Year, ~ Company, ~ Where, ~ Why,

  "Senior Data Scientist", "2018 - Present", "Edge By Ascential (formerly Clavis Insight)", "Dublin, Ireland",NA,
  "Data Scientist", "2016 - 2018", "", NA, 
  "Researching and implementing various statistical methods for use within ecommerce insights and analytics.",
 
 "Data Scientist", "2016 - 2018", "", NA, 
 "Developed API in R which uses supervised classification to remove manual data input and QA testing.",
 
 "Data Scientist", "2016 - 2018", "", NA, 
 "Created suite of UI's tailored for specific tasks within the organisation, allowing users to interactively manage data and apply machine learning techniques to simplify problems.",
 
 "Data Scientist", "2016 - 2018", "", NA, 
 "Created end to end process including GUI's to allow users easily perform intelligent text matching.",
 
 "Data Scientist", "2016 - 2018", "", NA, 
 "Supervised and delivered statistical analysis projects for clients.",
 
 "Data Scientist", "2016 - 2018", "", NA, 
 "Co-supervised Trinity College Dublin final year students projects in the areas of 
					machine learning and data analytics.",
 "", "", NA, NA, NA,
 
 "Lecturer - School of Mathematics and Statistics", "Autumn 2019", "University College Dublin", "Belfield, Dublin 4.",   
 "Prepared and recorded lectures for an online postgraduate module titled `Intro to Data Analytics'.",
 
 "Lecturer - School of Mathematics and Statistics", "Autumn 2019", "University College Dublin", "Belfield, Dublin 4.",   
 "Managed all continuous assessment and the final examination.",

 "Lecturer - Lochlann Quinn School of Business", "Spring 2019", "", "", 
 "Delivered lectures for an undergraduate module titled `Data Analysis for Decision Makers'.",
 
 "Lecturer - Lochlann Quinn School of Business", "Spring 2019", "", "", 
 "Helped to prepare, coordinate, and correct both the mid semester project and the final examination.",

 "Lecturer - School of Mathematics and Statistics", "Spring 2016", "", "", 
 "Lectured an online undergraduate module titled `Practical Statistics'.",

 "Lecturer - School of Mathematics and Statistics", "Spring 2016", "", "", 
 "Coordinated tutors and teaching assistants for computer labs in Minitab and R.",
 " ", " ", NA, NA, NA,
 
 "Postdoctoral Researcher", "2015 - 2016", "Insight Centre for Data Analytics & Clavis Insight", "Dublin , Ireland.", 
 "Researched text classification methods for use in ecommerce analytics.",
 
 "Postdoctoral Researcher", "2015 - 2016", "Insight Centre for Data Analytics & Clavis Insight", "Dublin , Ireland.", 
 "Involved research into both supervised and unsupervised text classification methods with the aim of solving an industry specific problem.",
 "  ", "", NA, NA, NA,
 
 "Tutor", "2010 - 2015", "University College Dublin", "Belfield, Dublin 4.", 
 "Tutored undergraduate and postgraduate students over a broad range of courses including probability theory, actuarial statistics, Bayesian analysis, data programming and multivariate analysis.",
 
 "Tutor", "2010 - 2015", "University College Dublin", "Belfield, Dublin 4.",
 "Demonstrated and tutored computer practical classes (SAS, R and Minitab) of up to fifty students for both undergraduates and postgraduates.",
 
 "Tutor", "2010 - 2015", "University College Dublin", "Belfield, Dublin 4.",
 "Graded undergraduate and postgraduate assignments in addition to final examinations.",
 
 "Tutor", "2010 - 2015", "University College Dublin", "Belfield, Dublin 4.",
 "Created screencasts and administered discussion boards for an online module: `Data programming with R'.",
 "", "  ", NA, NA, NA,
 
 "Statistical Consultant", "Summer 2012", "AOL", "Heuston South Quarter, Dublin 8.",
 "Undertook a three month study to create an algorithm to automatically detect spam searches on AOL's search engine.",
	              
) %>% 
  detailed_entries(Title, Year, Company, Where, Why, .protect = T)
```

\newpage

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Why,
  "PhD~in Computational Statistics", "2011 - 2015", "University College Dublin", "Dublin, Ireland",
  "Title: `Overcoming Intractable Likelihoods' (Supervisor: Prof.~Nial Friel).",
  "PhD~in Computational Statistics", "2011 - 2015", "University College Dublin", "Dublin, Ireland",
  "Improved simulation methods for estimating intractable likelihoods in area's such as spatial statistics and social network analysis.",
  
  "MSc~in Statistics (First Class Honours)", "2010 - 2011", "University College Dublin", "Dublin, Ireland",
  "Minor thesis: `Supervised Probabilistic Classification' (Supervisor: Prof.~Nial Friel).",
  "MSc~in Statistics (First Class Honours)", "2010 - 2011", "University College Dublin", "Dublin, Ireland",
  "Courses covered: Multivariate Analysis, Mathematical Statistics, Bayesian Analysis,
                 	Time Series Analysis, Applied Statistical Modelling, Data Programming,
                 	Monte Carlo Inference and Stochastic Models.",
  "BSc~in Mathematical Science (Upper Second Class Honours)", "2006 - 2011", "University College Dublin", "Dublin, Ireland", NA
) %>% 
  detailed_entries(Degree, Year, Institution, why = Why)
```


# Technical Skills

## Programming
\vspace{-0.2cm}  
- 10 years experience with R:  
    - Code in daily use within a production environment. 
    - Suite of UI applications developed using the Shiny library.
- Proficient in: Git, SQL (Postgres, MySQL), \LaTeX, Docker.
- Familiar with: AWS, command line tools, Python, HTML, C, SAS, SPSS.


## Methodologies
\vspace{-0.2cm}
- In depth knowledge of many statistical and machine learning techniques, including but not limited to:  
regression, MCMC, time series, principal component analysis, Bayesian inference, non-parametric methods, logistic regression/max ent, random forests, neural networks, LDA, k-means, nearest neighbour classifiers.



# Presentations

## Invited

```{r invited pres}
tribble(
  ~ when, ~ title, ~ details, ~ where, ~ url,
  "2019", "Data Scientist or Statistician?", 
  "Invited Speaker",  "Young-ISA meeting (Young section of the Irish Statistical Association)", "http://aboland.ie/docs/Young-ISA2019.html"
) %>%
  brief_entries(glue::glue("\\href{<url>}{\\textbf{<title>}} <where>", .open = "<", .close = ">"), when, 
                .protect = FALSE)
```

## Selected Others

```{r presentaions}
tribble(
  ~ when, ~ title, ~ details, ~ where, ~ url,
  "2018", "An R Case Study: From Research to Production", 
  "Poster Presentation",  "CASI 2018 (Conference on Applied Statistics in Ireland)",
  "http://aboland.ie/docs/casi_2018.html",
  
  "2017", "Using R to automate the classification of e-commerce products", 
  "Talk",  "EARL Boston (Enterprise Applications of the R Language)",
  "http://aboland.ie/docs/EARL2017.pdf",
  
  "2015", "Efficient MCMC for Gibbs Random Fields using pre-computation", 
  "Poster",  "Scalable Monte Carlo workshop at NIPS (Neural Information Processing Systems)",
  "http://aboland.ie/docs/NIPS2015.pdf",
) %>%
  brief_entries(glue::glue("\\href{<url>}{\\textbf{<title>}}, <where>", .open = "<", .close = ">"), when, .protect = FALSE)
```


# Publications
\vspace{2mm}


```{r publications}
tribble(
  ~ when, ~ title, ~ details, ~ where, ~ url,
  "2018", "Efficient MCMC for Gibbs Random Fields using pre-computation", 
  "\\textbf{Boland, A.}, Maire, F., Friel, N.",  "Electronic Journal of Statistics", "https://projecteuclid.org/euclid.ejs/1544670254",
  "2014", "Noisy Monte Carlo: convergence of Markov chains with approximate transitions kernels", 
  "Alquier, P., Friel, N., Everitt, R. and \\textbf{Boland, A.}",  "Statistics and Computing", "https://link.springer.com/article/10.1007/s11222-014-9521-x"
) %>%
  brief_entries(glue::glue("<details>, \\href{<url>}{\\textbf{<title>}} (\\textit{<where>})", .open = "<", .close = ">"), when, .protect = FALSE)
```

# Awards

```{r awards}
tribble(
  ~ when, ~ what,
  "2019", "\\href{https://community.rstudio.com/t/shiny-contest-winners-full-list/36347}{Shiny Contest} - 'Honorable Mention' for building an \\href{https://aboland.shinyapps.io/DublinTransport/}{Shiny app} which displays real time public transport info for Dublin.",
  "2016", "Awarded Graduate Statistician (GradStat) status by \\href{https://www.rss.org.uk/}{The Royal Statistical Society}."
) %>%
  brief_entries(glue::glue("<what>", .open = "<", .close = ">"), when, .protect = FALSE)
```



# Interests and Activities

I enjoy all kinds of sport. I am particularly interested in rugby, gaelic games, and golf. I played rugby until 2018, and I continue to play golf. I also enjoy exploring interesting datasets, developing R packages, and creating Shiny apps.






